Trends of SDR in Thessaloniki

### 2023-07-10 Article.Rmd
Commit 2023-07-10 18:14

```{r echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("./DHI_GHI_0_variables.R")

@@

@@

We group the anomaly data in $1^\circ$ SZA bins, and calculate the overall trend for each bin

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.35\\linewidth', out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrends-13.png")
knitr::include_graphics("./images/SzaTrends-17.png" )
knitr::include_graphics("./images/SzaTrends-21.png")
```

>>>>

```{r echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
## number of measurements
SDR_N_All   <- sum(  ALL_1_daily_DESEAS[,GLB_att_N])
SDR_N_Clear <- sum(CLEAR_1_daily_DESEAS[,GLB_att_N])
SDR_N_Cloud <- sum(CLOUD_1_daily_DESEAS[,GLB_att_N])

TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("./DHI_GHI_0_variables.R")

@@

Of the total 1-minute measurements
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$ 
is characterized with clear-sky conditon, and the rest 
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
with cloud-sky conditions.

@@

We group the anomaly data in $1^\circ$ SZA bins, and calculated the overall trend for each bin

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.35\\linewidth', out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrends-13.png")
knitr::include_graphics("./images/SzaTrends-17.png" )
knitr::include_graphics("./images/SzaTrends-21.png")
```
